---
title: "HW1"
author: "Jimmy Eriksson Widfors"
date: "9 november 2018"
output: github_document
---

#Version of R & packages

R version : 3.5.1
Packages  : "ggplot2", "readxl"

## Experience

I have used R-studio since 2014 to do assignments during courses I have taken in mathematical statistics at Stockholm University. I have somewhat experience of using R Markdown. I used it to do an assignment during the course called "Statistisk inferensteori". I have never used Git, Github, ggplot2 or dplyr before.




## Data

The dataset consist of the closing prices, and the corresponding dates, of the stock TELIA during the period 01-11-2017 - 01-11-2018. The data was downloaded from  http://www.nasdaqomxnordic.com/, and then imported to R-studio by using the package "readxl".

```{r,echo=FALSE}

library(readxl)



df <- read_excel("C:/Users/Jimmyew/Desktop/telia.xlsx")



```

## ggplot
Plotting the data using the package "ggplot2" with Closing-price on the y-axis and Date on the x-axis.


```{r,echo=FALSE}

library(ggplot2)

ggplot(df, aes(x = Date, y = `Closing price`)) +
  geom_point() +
  geom_smooth()



```


```{r}
sessionInfo()
```